Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-05 paper/main.tex
Auto Update from local Sharelatex

KFP addresses the issue of data access by generating faux-data that is ``statistically similar'' to the real data but does not itself contain any sensitive data. This faux-data can be analyzed, cleaned, feature-engineered, etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model. Three of these plug-ins are provided with full documentation for creating other plug-ins.

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}

Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented three plugins that use different techniques for data synthesis, as shown in Table~\ref{included-methods}. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al. \cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release. For SGF and DataSynthesizer, their authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}). In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard. Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.

\begin{table}
  \caption{Kung Faux Pandas data synthesis methods}
  \label{included-methods}
  \centering
  \begin{tabular}{p{12em} l p{14em}}
    \toprule
    Method                                 & Source                    & Notes \\
    \midrule
    Kernel Density Estimator               & scipy.stats.gaussian\_kde & Inter-related ordinal and ratio data\\
    DataSynthesizer                        & Ping et al.               & Bayesian modeling of column relationships\\
    Synthetic dataset Generation Framework & Bindschaedler et al.      & "Plausible Deniability" probabilistic modeling\\
    \bottomrule
  \end{tabular}
\end{table}

@@

>>>>

KFP addresses the issue of data access by generating faux-data that is ``statistically similar'' to the real data but does not itself contain any sensitive data. This faux-data can be analyzed, cleaned, feature-engineered, etc. as if it were the actual source data. KFP provides a standard mechanism for wrapping a privacy protection method into a plug-in which integrates the method with the Pandas DataFrame model. Two of these plug-ins are provided with full documentation for creating other plug-ins.

@@

Figure~\ref{fig:synthesis_process} provides a detailed look at the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. 
\begin{figure}[ht]
  \centering
  \includegraphics[width=120mm]{data_synthesis_process}
  \caption{Data synthesis process.}
  \label{fig:synthesis_process}
\end{figure}
All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, machine learning developers or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented two plugins that use different techniques for data synthesis. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

@@

% include some of this? 
% Lastly, the Synthetic dataset Generation Framework (SGF) by Bindschaedler et al. \cite{Bindschaedler2017} "generates differentially private synthetic data" using a novel criterion called plausible deniability that is applied to a dataset before it is deemed safe to release.  In the case of SGF, several models are built with both real and synthetic data and compared against a gold standard. Their author's analysis showed that the models from synthetic data are close to the same accuracy as models built with real data.
